Twisted \(M\)-theory and its perturbative quantization.

### 2020-11-27 paper.tex
paper

\def\pv{{\rm PV}}

@@

\section{Quantization of holomorphic-topological theories}
\label{sec:org297a559}
\subsection{Effective renormalization}
\label{sec:orga5cd4ed}
\subsection{The \(11\)-dimensional theory}
\label{sec:org8b189fc}
\subsection{The moduli space of quantizations}
\label{sec:orgf278b4e}
\section{Relationship to the Type IIA string}
\label{sec:org355a726}
In the remainder of the paper, we wish to establish various consistency checks corroborating the claim that the 11d theory of interest describes a twist of 11d supergravity. In this section, we demonstrate that this claim is consistent with a conjectural description of a twist of type IIA supergravity due to \cite{}.

Before recalling this conjecture, we first fix some notation. For a complex manifold $X$, let $TX$ denote the holomorphic tangent bundle and define
\[
\pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX) .\]
This is the space of $i$-pvvectors of Dolbeault type $j$.
Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields of type $i$.

@@

With this in hand, the conjecture of \cite{} is as follows:

\begin{conj}
  [Costello-Li \cite{}]
  Let $(M,h_{M})$ be a Kahler surface and $(X, h_{X})$ be a Calabi-Yau 4-fold. Consider perturbative type IIA supergravity on $M\times X$ around a background where the graviton is set to $h_{M}+ h_{X}$, the bosonic ghost for local supersymmetries takes a VEV $Q$ that is invariant for the $\SU(4)$ subgroup of isometries preserving $X\subset M\times X$, and all other background fields are set to zero. The resulting theory admits a description as a Poisson BV theory with fields $\Omega^{\bullet}(M)\otimes \pv^{\bullet, \bullet}(X)[\![t]\!]$ where $t$ is a parameter of degree 2, $L_{\infty}$-structure given by $\ell_{1} = d\otimes 1+ 1\otimes (\dbar+t\partial)$, $\ell_{2} = \wedge\otimes \{-,-\}_{\rm NS}$ and Poisson kernel given by $(1\otimes \partial)\delta_{\Delta(X)}\delta_{\Delta (M)}$.
\end{conj}

Type II supergravity around such backgrounds where the bosonic ghost takes a nonzero VEV is what the authors call twisted supergravity. In fact, the authors further conjecture that type IIA superstring theory on $M\times X$ around a particular Ramond-Ramond background is equivalent to a topological string theory given by the A-model on $M$ and the B-model on $X$. This implies the above conjecture at the level of closed string field theory. Indeed the above description of twisted supergravity is a combination of Kodaira--Spencer theory on $X$ with the zero-winding sector of Kahler gravity on $M$.

The authors of \cite{} establish a strand of evidence via residual supersymmetry. Namely, they construct an $L_{\infty}$ map from the $Q$-cohomology of the 10d $\cN = (1,1)$ algebra to the fields of the above theory, realizing the former as a collection of ghosts in the latter. This allows us to make sense of further twists of the above twist.

@@

\subsubsection{Eight-dimensional Kodaira--Spencer theory}
\label{sec:orgeb2dd4d}
\subsection{The Type IIA topological string}
\label{IIAtop}
\subsection{Reduction of twisted supergravity}
\label{sec:orgcf7b6a4}
\subsubsection{Calabi--Yau compactifications}
\label{sec:org16a2c98}
\subsection{Twisted supergravity on a three-fold}
\label{sec:org774abb4}
\section{The non-minimal G2 twist}
\label{sec:org590ab85}
Does math mode \(work here = e^x\)?
\end{document}

>>>>

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}

@@

\section{Quantization of holomorphic-topological theories}
\label{sec:org297a559}
\subsection{Effective renormalization}
\label{sec:orga5cd4ed}
\subsection{The \(11\)-dimensional theory}
\label{sec:org8b189fc}
\subsection{The moduli space of quantizations}
\label{sec:orgf278b4e}
\section{Relationship to the Type IIA string}
\label{sec:org355a726}
In the remainder of the paper, we wish to establish various consistency checks corroborating the claim that the 11d theory of interest describes a twist of 11d supergravity. In this section, we demonstrate that this claim is consistent with a conjectural description of a twist of Type IIA supergravity due to \cite{CLsugra}.

Before recalling this conjecture, we first fix some notation which is useful to describe the state space for the Type IIA string.
For $i,j$ integers define the space of $(i,j)$-polyvector fields to be
\[
  \pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX)
\]
where $TX$ is the holormorphic tangent bundle.
Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields $\PV^{i}_{\rm hol}(X)$ of type $i$.

@@

There is compelling evidence \cite{CLsugra} for the existence of a twist of the Type IIA string on the ten-manifold $M \times X$ where $M$ is a real surface and $X$ is a Calabi--Yau four-fold.
Roughly, the twist behaves like the A-model topological string along $M$ and the $B$-model topological string along $X$.
The conjectural state space is
\[
  \Omega^\bu(M) \; \Hat{\otimes} \; \PV^{\bu, \bu} (X) .
\]
The linear BRST differential on this state space is given by $\d_{\rm dR} + \dbar$.
The fields of the closed string are given by the $S^1$-equivariant states, which is modeled \cite{CLbcov} by
\[
  \Omega^\bu(M) \; \Hat{\otimes} \; \PV^{\bu, \bu} (X) [\![u]\!]
\]
where $u$ is the equivariant parameter and the new linear BRST operator is $\d_{\rm dR} + \dbar + u \partial_\Omega$.

With this informal description of the twist of the Type IIA closed string in hand, one can deduce the following low energy limit of the description which gives a conjectural description of Type IIA supergravity.

\begin{conj}
  [Costello-Li \cite{CLsugra}]
  Let $(M,h_{M})$ be a Kahler surface and $(X, h_{X})$ be a Calabi-Yau 4-fold.
  Consider perturbative type IIA supergravity on $M\times X$ around a background where:
  \begin{itemize}
    \item the graviton is set to $h_{M}+ h_{X}$,
    \item the bosonic ghost for local supersymmetries is set to a covariantly constant square-zero spinor $Q$ that is invariant for the $\SU(4)$ subgroup of isometries preserving $X\subset M\times X$,
    \item all other background fields are set to zero.
  \end{itemize}
  In this background, the resulting theory is equivalent to the Kodaira--Spencer type theory whose fields are
  \[
    \Omega^{\bullet}(M) \; \Hat{\otimes} \; \PV^{\bullet, \bullet}(X)[\![u]\!]
  \]
  where $u$ is a parameter of cohomological degree $2$.
  \brian{this theory is only $\ZZ/2$-graded, right?}
  %$L_{\infty}$-structure given by $\ell_{1} = d\otimes 1+ 1\otimes (\dbar+t\partial)$, $\ell_{2} = \wedge\otimes \{-,-\}_{\rm NS}$ and Poisson kernel given by $(1\otimes \partial)\delta_{\Delta(X)}\delta_{\Delta (M)}$.
\end{conj}

Type II supergravity around such backgrounds where the bosonic ghost takes a nonzero VEV is what is referred to as {\em twisted supergravity} in \cite{CLsugra}.
In fact, the authors further conjecture that type IIA superstring theory on $M\times X$ around a particular Ramond-Ramond background is equivalent to a topological string theory given by the A-model on $M$ and the B-model on $X$.
This implies the above conjecture at the level of closed string field theory.
Indeed the above description of twisted supergravity is a combination of Kodaira--Spencer theory on $X$ with the zero-winding sector of Kahler gravity on $M$.

There is further evidence for this claim through studying the residual supersymmetry.
Namely, they construct an $L_{\infty}$ map from the $Q$-cohomology of the 10d $\cN = (1,1)$ algebra to the fields of the above theory \cite{CLsugra}, realizing the former as a collection of ghosts in the latter. This allows us to make sense of further twists of the above twist.

@@

\subsubsection{Eight-dimensional Kodaira--Spencer theory}
\label{sec:orgeb2dd4d}
\subsection{The Type IIA topological string}
\label{IIAtop}
\subsection{Reduction of twisted supergravity}
\label{sec:orgcf7b6a4}
\subsubsection{Calabi--Yau compactifications}
\label{sec:org16a2c98}
\subsection{Twisted supergravity on a three-fold}
\label{sec:org774abb4}
\section{The non-minimal G2 twist}
\label{sec:org590ab85}

\brian{some general background on G2 twist, state main result}

We consider the eleven-dimensional theory on the space
\[
  X \times Z \times \RR
\]
where $Z$ is a hyper-K\"{a}hler surface and $X$ is a Calabi--Yau three-fold.
Denote by $\Omega_Z$ the holomorphic volume form on $Z$ and $\Omega_X$ the holomorphic volume form on $X$.
We will work in a background where the $(1,0)$-component of the field $\gamma$ satisfies the following equations:
\begin{equation}\label{eqn:background}
  \begin{array}{rcccc}
    \partial \gamma^{1,0} & = & \Omega_Z \\
    \dbar \gamma^{1,0} + \d_{\rm dR} \gamma^{1,0} & = & 0 .
  \end{array}
\end{equation}
The second equation implies that $\gamma^{1,0}$ is constant along $\RR$ and holomorphic along $X \times Z$.
The first equation says that $\gamma^{1,0}$ is a trivialation of the holomorphic volume form on $Z$.

To see that this is a consistent background of the eleven-dimensional theory we must check that $\gamma^{1,0}$ satisfies the appropriate equations of motion.

\begin{lem}
  Any field $\gamma^{1,0}$ satisfying the equations in (\ref{eqn:background}) satisfies the Maurer--Cartan equation of the eleven-dimensional theory.
\end{lem}

\begin{proof}
  We must show that $\gamma^{1,0}$ satisfies the following Maurer--Cartan equation
  \[
    Q_{\rm BRST} \gamma^{1,0} + \frac12 [\gamma^{1,0} ,\gamma^{1,0}] = 0
  \]
  where $Q_{\rm BRST}$ is the linear BRST operator and $[-,-]$ is the Lie bracket defining the interacting piece of the eleven-dimensional theory.

  Recall, the linear BRST differential is of the form
  \[
    \dbar + \partial_{\Omega} + \partial_{\Omega^0 \to \Omega^1} + \d_{\rm dR}
  \]
  Here, $\partial_\Omega$ is the divergence operator which only acts on the $\mu$-type fields and $\partial_{\Omega^0 \to \Omega^1}$ is the first piece of the holomorphic de Rham operator acting on $\Omega^{0,\bu}(X \times Z)$.
  Since $(\dbar + \d_{\rm dR}) \gamma^{1,0} = 0$ by assumption, we see that $\gamma^{1,0}$ is closed for the linear BRST operator.

  The only component of the Lie bracket involving two fields of type $\gamma$ is of the form
  \[
    [\gamma, \gamma] = (\partial \gamma \wedge \partial \gamma) \vdash \Omega \in \PV^{1,\bu}(X \times Z) \; \Hat{\otimes} \; \Omega^\bu(L) .
  \]
  Since $\partial \gamma^{1,0}$ is a $(2,0)$ form along $Z$, we see that $\partial \gamma^{1,0} \wedge \partial \gamma^{1,0} =0$.
  We conclude that $\gamma^{1,0}$ satisfies the Maurer--Cartan equation.
\end{proof}

Next, we expand the action functional near the background where $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ where $\gamma^{1,0}$ satisfies equations (\ref{eqn:background}).
This will generate new kinetic and interacting terms which we can extract by inserting a formal parameter $\delta$ and expression the action functional in terms of the deformed field $\Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.

There are two interaction terms
\begin{equation}\label{eqn:int1}
  \frac12 \int_{X\times Z \times L} \left(\gamma \vee \{\mu, \mu\} \right) \wedge (\Omega_Z \wedge \Omega_X)
\end{equation}
and
\begin{equation} \label{eqn:int2}
  \frac16\int_{X \times Z \times L} \gamma \partial \gamma \partial \gamma .
\end{equation}

We can integrate Equation (\ref{eqn:int1}) by parts to put it in the form $\frac12 \int_{X \times Z \times L} \left[(\partial \gamma) \vee (\mu \wedge \mu) \right]$ where $\mu \wedge \mu$ is the wedge product of polvector fields.
Expanding this expression around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$ we obtain
\[
  \frac12 \int \left(\gamma \vee \{\mu, \mu\} \right) \wedge (\Omega_Z \wedge \Omega_X) + \frac{\delta}{2} \int \left[\Omega_Z \vee (\mu \wedge \mu) \right] \wedge (\Omega_Z \wedge \Omega_X) .
\]
Here, we have used the identity $\partial \gamma^{1,0} = \Omega_Z$.

Next, we expand Equation (\ref{eqn:int2}) around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
This becomes
\[
  \frac16 \int \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \left(\gamma \partial \gamma\right) \wedge \Omega_Z .
\]
Notice that there are no $\delta^2$ terms since $\partial \gamma^{1,0} \partial \gamma^{1,0} = 0$.

So far, we have written everything in terms of action functionals.
There is a completely equivalent statement in terms of the resulting dg Lie algebra structure describing the eleven-dimensional theory in this background which we summarize as follows.

\begin{lem} \label{lem:background}
  The dg Lie algebra describing the eleven-dimensional theory placed in a background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is isomorphic to the the dg Lie algebra whose differential is
  \begin{equation}\label{eqn:newdiff}
    Q_{\rm BRST} + \frac{1}{2} \left\{ \int \left[\Omega_Z \vee (\mu \wedge \mu) \right] \wedge (\Omega_Z \wedge \Omega_X) + \int \left(\gamma \partial \gamma\right) \wedge \Omega_Z , \; - \; \right\}
  \end{equation}
  and whose Lie bracket is unchanged.
  Here, $Q_{\rm BRST}$ is the original linear BRST differential of the eleven-dimensional theory.
\end{lem}

This lemma followed directly from our analysis of the way the action functional of the theory decomposed around the background.
The next result we state is an equivalence with a theory which exists on any product of manifolds $Z \times M$ where $Z$ is a hyper-K\"{a}hler surface as above but now $M$ is any smooth seven-dimensional manifold.

\begin{prop}
  The eleven-dimensional theory on $X \times Z \times L$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is equivalent to the theory whose fields are
  \[
    \alpha \in \Omega^{0,\bu}(Z) \; \Hat{\otimes} \; \Omega^\bu(X \times L)
  \]
  and whose action functional reads
  \[
    \frac12 \int \alpha \d\alpha + \frac16 \int \alpha \{\alpha, \alpha\}
  \]
  where $\{-,-\}$ is the Poisson bracket on $\Omega^{0,\bu}(Z)$.
\end{prop}

As stated above, this theory clearly does not depend on the complex structure on the Calabi--Yau three-fold $X$.
The theory only depends on the smooth structure on $M = X \times L$.
\brian{cite Surya and Phil, Chris and B, Kevin}

\begin{proof}
To unpack this new differential (\ref{eqn:newdiff}) as in Lemma \ref{lem:background} we need to reidentify the fields of the eleven-dimensional theory.
First, note that we have natural identifications
\begin{align}
  \PV^{1,\bu}(X \times Z) & = \PV^{1,\bu}(X) \; \Hat{\otimes} \; \PV^{0,\bu}(Z)\; \oplus \; \PV^{0,\bu}(X) \; \Hat{\otimes} \; \PV^{1,\bu}(Z) \\ & \cong \Omega^{2,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu} (Z) \; \oplus \; \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z) \label{eqn:decomposevf}
\end{align}
The isomorphism uses both the holomorphic volume forms $\Omega_X$ and $\Omega_Z$.

From Lemma \ref{lem:background} we see that the new terms in the linear BRST differential arise from the quadratic terms in the action
\begin{equation}\label{eqn:newterms}
  \int \left[\Omega_Z \vee (\mu \wedge \mu) \right] \wedge (\Omega_Z \wedge \Omega_X) + \int \left(\gamma \partial \gamma\right) \wedge \Omega_Z .
\end{equation}

Recall that the linear BRST complex of the original eleven-dimensional theory is obtained by taking the tensor product of the cochain complexes $\PV^{1,\bu}(X \times Z) \xto{\partial_\Omega} \PV^{0,\bu}(X \times Z)$ and $\Omega^{0,\bu}(X \times Z) \xto{\partial} \Omega^{1,\bu}(X \times Z)$ with the de Rham complex $\Omega^\bu(L)$ on the one-manifold $L$.

Using the decomposition (\ref{eqn:decomposevf}) we see that the deformed linear BRST complex takes is the tensor product of the de Rham complex $\Omega^{\bu}(L)$ with the cochain complex
\[
  \begin{tikzcd}
  & \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z) \ar[dr, "\partial_Z"] \\
  & & \Omega^{3,\bu}(X) \; \Hat{\otimes} \; \Omega^{2,\bu}(Z) \\
 & \Omega^{2,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu}(Z) \ar[ur, "\partial_X"'] & \\
\;_{\cong}  & & \Omega^{1,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu}(Z) \ar[ul, dashed, bend left = 10, "\partial_X"]\\
 & \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu}(Z) \ar[ur, "\partial_X"] \ar[dr,"\partial_Z"'] \\
  & & \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z)
\ar[dashed, rounded corners, to path={ -- ([yshift=-2ex]\tikztostart.south) -| ([xshift=-1.5ex]\tikztotarget.west) -- (\tikztotarget)}, uuuuul]
  %\ar[uuuuul, start anchor =  {[yshift = 0ex, xshift=0ex]}, end anchor = {[yshift=1.0ex, xshift=-5ex]}, bend left = 90, dotted] .
  \end{tikzcd}
\]
Here, the dashed arrow along the outside of the diagram corresponds to the BV antibracket with the first term in (\ref{eqn:newterms}).
Note that this is the identity morphism on $\Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z)$.
The other dashed arrow corresponds to the BV antibracket with the second term in (\ref{eqn:newterms}).
It is given by the holomorphic de Rham operator $\partial_X : \Omega^{1,\bu}(X) \to \Omega^{2,\bu}(X)$.

\brian{cochain homotopy finish}
Since the outer dashed arrow is an isomorphism, we see that this cochain map is a quasi-isomorphism.
It is immediate to check that this quasi-isomorphism intertwines the Lie brackets.

\end{proof}

\end{document}
